Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
remove completeness claim from intro

We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
both based on the CounterExample Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
We provide two alternative automated procedures to synthesise safe digital state-feedback controls, 
and alongside completeness \todo{are we actually complete? for instance, abstraction refinement might not be successful (we do TO)} we prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant. 
% computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.

@@

>>>>

We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
both based on the Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
We provide two alternative automated procedures to synthesise safe 
digital state-feedback controls
and prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant. 
% computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.

@@

We implemented both our approaches and provide experimental proof 
that, while the naive approach does manage to synthesize 
stable and sound controllers for the majority of our benchmarks
for a set of intricate physical plant models taken from the digital 
control literature

it is an order of magniture slower than the abstraction-based one.

showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is $7.9$ seconds, and most controllers can be synthesized in less
than $17.2$ seconds.
